\font\sixrm=cmr6
\font\mainfont=cmr12
\font\mi=cmti12
\font\mb=cmbx12
\font\sectionfont=cmbx12
\font\headingfont=cmbx12
\font\titlefont=cmbx12

\def\RCS$#1: #2 ${\expandafter\def\csname RCS#1\endcsname{#2}}


\def\heading#1{\vskip 12 pt \leftline{\headingfont #1}}

\newcount\footnotes \footnotes=0

\def\footnoter#1{\advance\footnotes by 1 \footnote{$^{\the\footnotes}$}{\mainfont #1}}

\def\section#1{\vskip 12 pt \leftline{\sectionfont #1}}

\def\title#1{\centerline{\titlefont{#1}} \footline{\hss\tenrm{#1:} Page \folio\hss}}

\newcount\itemnum

\def\items{\advance\itemnum by 1 \itemitem {\the\itemnum)}}
\def\topic#1{\itemitem {\mb #1:}}
\def\dashtopic{\itemitem {\mb -}}
\def\pskip{\parskip 12 pt}
\def\lskip{\parskip 3pt}
\def\sskip{\parskip 6pt}

\def\ATL{Atlassian Pty Ltd}
\def\DOT{Dot Communications Pty Ltd}
\def\UOW{University of Wollongong}
\def\FST{Fluffy Spider Technologies Pty Ltd}
\def\dZN{de Zwart Networks}

\pskip
\parindent 24 pt

\title{Peter de Zwart's Curriculum Vit\ae}

\mainfont

\heading{Personal Details}

\topic{Name} Peter de Zwart {\mi BCompSci(SDS)}
\lskip
\topic{Mobile} +61 4 1164 8655
\topic{e-mail} curriculum.vitae@dezwart.net.au
\pskip

\heading{Key Strengths}

\dashtopic Highly proficient with {\mb Linux/Unix} environments, obtained through over 12 years of experience.
\lskip
\dashtopic Enjoy designing solutions to problems \& following them through to completion, from an inherent desire to improve the status quo.
\dashtopic Ability to take complex topics \& explain them in simple terms, learnt through academic tutoring.
\dashtopic Enjoy researching topics so that new knowledge can be applied to current projects.
\dashtopic Good technical documentation skills, from writing change control requests, installation documentation \& operation procedures.
\dashtopic Excellent verbal communications skills, from liaising with customers \& suppliers in regards to costing \& issue mitigation.
\pskip

\heading{Overview}

A {\mb systems administrator} \& {\mb programmer}, with over 12 years experience in the IT\&T industry; involving work in both the private \& academic sectors. Having worked on high-availability Internet service platforms, software development infrastructure, systems \& application programming, \& teaching students in an academic environment.

The roles that I have chosen have allowed me to enjoy a variety of perspectives, as it has exposed me to many levels of corporation management; from working on the line to reporting to directors at board meetings.

I'm looking for a career where I can be a part of something larger than myself, providing infrastructure services to communities involved in scientific research or society as a whole.

\heading{Skills \& Experience}

$$\vbox{\settabs 2 \columns
\+Bash \& Shell Scripting&C \& C++ Programming\cr
\+Config automation: Puppet, Bcfg2, \&c...&RHEL \& Debian based Linux Administration\cr
\+Java Programming&Python, PHP, Perl \& Ruby Scripting\cr
\+TCP/IP Networking&CISCO Routers, ICND2\cr
\+SVN, Git \& CVS Source Control&SQL99\cr
\+XML \& various markup languages &Maven 2\cr
\+\TeX Programming&Vi Editor\cr
\+VMWare, OpenVZ, Xen virtualisation&OmniGraffle Diagramming\cr
\+Microsoft Batch Programming&Installation Automation\cr
\+Monitoring tools: Cacti, Nagios, Smokeping, Munin, Pingdom, NewRelic RPM&\cr
}$$

\eject

\heading{Professional History}

\section{\ATL}

\lskip
\topic{Role} Systems Engineer
\topic{Dates} 06/2010 - Present
\topic{Reported to} Systems Engineering Lead
\topic{Achieved} Established a service catalogue for the IT department to ensure SLAs were measurable.
\dashtopic Established service on-boarding/off-boarding procedures to ensure service SLAs were attainable.
\dashtopic Established service monitoring based upon the service catalogue \& monitoring policy to ensure service SLAs were measured \& incidents reported.
\dashtopic Established staff entry \& exit procedures.
\dashtopic Established installation procedures for OpenVZ Hardware Nodes \& Containers to allow for horizontal scaling of Atlassian's build \& service systems.
\dashtopic Helped change the attitude of the Systems Administration team to convert Atlassian's history of tribal knowledge to written information \& procedures that can be relied upon.
\topic{Duties} Planning \& executing projects around our critical production systems.
\dashtopic Monitoring, maintaining \& optimising those systems.
\dashtopic Working closely with developers \& other staff to solve operational issues with our applications.
\dashtopic Scheduling, coordinating \& communicating maintenance windows for critical systems.
\dashtopic Coordination with our colocation providers.
\dashtopic Ensuring the security of our critical systems.
\dashtopic Senior First Aid officer.
\dashtopic Area Fire Warden.
\pskip

\topic{Role} QA Engineer
\lskip
\topic{Dates} 08/2008 - 06/2010
\topic{Reported to} QA Lead
\topic{Achieved} Designed \& implemented an infrastructure \& build configuration/scripting to support continuous integration testing of Atlassian's software products within supported platforms. Automated software installation \& configuration based on modularised environment components, with heavy leveraging of virtualisation technologies.
\topic{Duties} Stability \& penetration testing of Atlassian's software, on an as-needed basis.
\dashtopic SME for automated testing \& virtualised environments.
\dashtopic Senior First Aid officer.
\dashtopic Area Fire Warden.
\topic{Reason left} Determined I had greater value to the company as a Systems Engineer.

\section{\DOT}

\lskip
\topic{Role} Solutions Engineer
\topic{Dates} 11/2006 - 08/2008
\topic{Reported to} Product Manager
\topic{Achieved} Co-development of a Virtual Server Provisioning System\footnoter{http://ultimoroad.com/bonbon/} based on Xen using J2EE technology, to assist the Development \& QA Departments to perform automated testing.
\dashtopic Co-development of a MySQL InnoDB snapshot system to significantly reduce load-times associated with loading production datasets.
\dashtopic Regular developer blog entries regarding the above, helping to promote the internal product.
\dashtopic Establishment of Demonstration Systems for use by Sales \& Marketing staff, leveraging virtualisation technologies.
\topic{Duties} Assisting both the Operations \& Development Departments by integrating the Wholesale Service Delivery Platform Software with the Service Management Platforms.
\dashtopic Gathering internal requirements from the Project Manager for customer solutions; designing, documenting, implementing \& delivering the final solution to the Operations Department, then assisting with the integration testing.
\dashtopic Subversion \& Maven repository management.
\topic{Reason left} Opportunity at \ATL.
\pskip

\topic{Role} Operations Manager
\lskip
\topic{Dates} 08/2005 - 11/2006
\topic{Reported to} Product Manager
\topic{No. of Staff} 5
\topic{Achieved} Provided a capacity management plan to the Board of Directors that allowed growth of the largest Service Management Platform from 40,000 Services in Operation to 120,000 within twelve months.
\dashtopic Design, costing, hardware acquisition \& project management of the hardware roll-out for a new Service Management Platform, able to sustain up to 250,000 services in operation.
\dashtopic Establishment of a Standard Operating Environment across all new server roll outs.
\dashtopic Change from a reactive approach to platforms management, to a communal pro-active approach by encouraging all Operations Team members to take part in the design, planning \& implementation phases.
\dashtopic Creation of departmental policies for Backup Systems, On-call duties, Off-site networks, SLA management \& issue mitigation.
\topic{Duties} Day-to-day management of the Operations Department, covering all Service Delivery Platforms supporting in excess of 200,000 Services in Operation, Australia Wide.
\dashtopic Leading a team of 5 Systems Operators, by providing project management, conflict resolution \& regular reports to upper management on a weekly basis.
\dashtopic Ensuring operational capability for meeting contracted Service Level Agreements with customers.
\dashtopic Engaging with our suppliers to ensure continuity \& quality of service to reach SLA KPIs.
\dashtopic Chairing weekly meetings of the Operations Department.
\dashtopic Writing Standard Operating Procedures for regular tasks that were conducted by team members.
\topic{Reason left} Solutions Team Established.
\pskip

\topic{Role} Systems Administrator
\lskip
\topic{Dates} 10/1998 - 12/2000 \& 12/2002 - 02/2003
\topic{Reported to} General Manager
\topic{Achieved} Consolidation of an aging ad-hoc network comprising of Slackware 1, Windows NT \& Windows 95 based servers on to two managed Red Hat Linux 5.2 servers.
\dashtopic Migration from static routing to BGP \& OSPF via multiple up-stream providers to allow for greater route redundancy \& fault tolerance.
\topic{Duties} Management \& maintenance of a collection of Linux servers \& Cisco routers providing dial-up access \& associated Internet based services to 2,000 end-users.
\dashtopic Area Fire Warden.
\topic{Reason left} Continue University Studies.
\pskip

\section{\UOW}

\lskip
\topic{Role} Part-Time Teaching Academic
\topic{Dates} 08/2002 - 06/2004
\topic{Reported to} Subject Co-ordinators
\topic{Achieved} The establishment of an improved marking scheme for the 2$^{nd}$ year Computer Science core subject ``The C Family \& Unix'' with the other tutors.
\topic{Duties} Tutoring for 1$^{st}$, 2$^{nd}$ \& 3$^{rd}$ year Computer Science \& Information Technology subjects performing the following: Computer Laboratory Demonstration, Tutorials, marking of papers, assistance in assignment \& assessment creation.
\dashtopic Duty of care for classes of 35 students in regards to OH\&S.
\topic{Reason left} Finished Bachelors Degree.
\pskip

\section{\FST}

\lskip
\topic{Role} Software Engineer
\topic{Dates} 05/2001 - 01/2002
\topic{Reported to} CEO
\topic{Achieved} Creation of a cross-architecture build environment, from i386 to ARM, \& live-cd build system emulating the functionality of a hand held device.
\dashtopic Establishment of a Standard Desktop Linux Image based on Debian {\mi Potato}.
\dashtopic Customer network deployment \& management based on the Standard Desktop Image to facilitate Voice Transcription of non-English languages.
\dashtopic Wrote a theme editor for IceWM in C/GTK for a hand held device.
\dashtopic Added city/point selection support to CDE Sunclock.
\topic{Duties} CVS Repository Management, Office Network Administration, Project based programming tasks.
\dashtopic Office Desktop Linux Support.
\topic{Reason left} Continue University studies.
\pskip

\section{\dZN}

\lskip
\topic{Role} Owner/Sole Proprietor
\topic{Dates} 01/2001 - Present
\topic{Reported to} Customers \& Self
\topic{Achieved} Based on the requirements of the customer, development of a database system for storage of Australian located lightning strikes, written in C. Needing to support a continuous live data feed, with a PHP web front-end for data queries. This allowed the customer to start the transition from a proprietary data distribution system to an XML based web-service.
\dashtopic Development of a CD-ROM firewall based on Debian {\mi Potato} used by clients before Linux based routing appliances were available \& economical.
\topic{Duties} Administration of a small business.
\dashtopic Requirements gathering for customer projects.
\pskip

\heading{Education}

\section{\UOW}

\lskip
\topic{2004} Bachelor of Computer Science, Secure Distributed Systems specialisation.
\topic{1998} University Entrance Diploma.
\pskip

\heading{Interests}

I have a keen interest in many aspects of science with a focus on astrophysics, sustainable energy, computational efficiency.

Other interests involve engineering, economics, automobile mechanics, tropical aquaculture, science fiction \& human languages.

\heading{References}

References can be provided upon request.

\bye
