\font\sixrm=cmr6
\font\mainfont=cmr10
\font\mi=cmti10
\font\mb=cmbx10
\font\sectionfont=cmbx12
\font\headingfont=cmbx12
\font\titlefont=cmbx12

\def\heading#1{\vskip 12 pt \leftline{\headingfont #1}}

\newcount\footnotes \footnotes=0

\def\footnoter#1{\advance\footnotes by 1 \footnote{$^{\the\footnotes}$}{\mainfont #1}}

\def\section#1{\vskip 12 pt \leftline{\sectionfont #1}}

\def\title#1{\centerline{\titlefont{#1}} \footline{\hss\tenrm{#1:} Page \folio\hss}}

\def\tw#1{\tt{#1}\mainfont}
\def\XX#1{\tw{-XX:#1}}
\def\I{\item -}
\def\II{\itemitem -}

\def\pskip{\parskip 12 pt}
\def\lskip{\parskip 3pt}
\def\sskip{\parskip 6pt}

\pskip
\parindent 24 pt

\title{Java Performance}

\mainfont

\heading{Scribbled Notes}

\I Memory mapped.
\lskip
\I Try HotSpot debug vm with \XX{+PrintInterpreter}
\I Native C stack.
\I Semantic.
\I Stack unwinding.
\I Stack frame.
\I \XX{-UseBiasedLocking}.
\I Fast-path code.
\I C1 JIT "\tw{-client}".
\I C2 JIT "\tw{-server}".
\I Mark word.
\I Thread local storage.
\I \tw{java.lang.Object.wait()}.
\I Threads lock.
\I Safepoints.
\I HotSpot VM C/C++ heap.
\II Arena.
\II Chunks.
\II ChunkPools. 3 Sizes.
\I Heap.
\I \XX{ErrorFile=}
\I \XX{OnError=}
\I \XX{+ShowMessageBoxOnError}
\I Stack overflow.
\I \XX{OnOutOfMemoryError=}
\I JConsole.
\I Weak Generational Hypothesis.
\I Card Table:
\II Card: 512 byte chunk of old gen.
\II Table: Array of one byte per card in heap.
\I Write barrier.
\I Premature promotion.
\I Promotion failure.
\I Bump the pointer.
\I TLAB: Thread Local Allocation Buffer.
\I Sliding compacting mark-seep (mark-compact).
\I CMS free lists.
\I G1GC, garbage first garbage collector.
\I CMS old gen occupancy.
\I CMS initiating limit.
\I TrainGC.
\I Calling conventions.
\I Compiler:
\II Front end.
\II Back end.
\II Intermediate Representation (IR).
\II Static Single Assignment (SSA).
\I Register Spilling:
\II Round robin local allocator.
\II Graph colouring.
\II Linear scan register allocation.
\I Class Heirachy Analysis (CHA).
\I Deoptimistaion:
\II Compiled frame.
\II Interpreted frame.
\I Compilation policy:
\II Invocation counter.
\II Backedge counter.
\I Bytecode index.
\I Compile threshold:
\II \tw{-Xbatch}.
\II \XX{-BackgroundCompilation}.
\I On Stack Replacement (OSR).
\I Uncommon traps.
\I Method liveness.
\I Code cache.
\I OopMaps.
\I x86 SSE.
\I Program dependence graph.
\I \tw{methodDataOop}.
\I Loop unswitching.
\I Loop unrolling.
\I Range check elimination.
\I Iteration splitting:
\II Preloop.
\II Main loop.
\II Post loop.
\I Superword.
\I \tw{nmethod}.
\I Tiered compilation:
\II \XX{+TieredCompilation} 6u25+.
\I Adaptive tuning, ergonomics.
\I \tw{Runtime.availableProcessors()}.
\I Adaptive heap sizing.
\I \XX{-UseAdaptiveSizePolicy}.
\I Performance monitoring.
\I Performance profiling.
\I Performance tuning.
\I \XX{+ScavengeBeforeFullGC}.
\I \XX{+PrintGCDetails}.
\I \tw{PSYoungGen}.
\I \tw{ParNew}.
\I \tw{DefNew}.
\I \tw{PSOldGen}.
\I \tw{PSPermGen}.
\I \XX{+UseParNewGC}.
\I \XX{+PrintTenuringDistribution}.
\I Concurrent mode failure.
\I \XX{+PrintGCTimeStamps}.
\I \XX{+PrintGCDateStamps}.
\I \tw{-Xloggc:<filename>}:
\II With \XX{+PrintGCDetails} \& \XX{PrintGCTimeStamps}.
\I \XX{+PrintGCApplicationConcurrentTime}.
\I \XX{+PrintGCApplicationStoppedTime}.
\I Full GC (System).
\I GCHisto.
\I Expected initial mark \& remark phase pauses less than minor collection.
\I VisualGC \tw{http://java.sun.com/performance/jvmstat}.
\I VisualVM \tw{http://visualvm.dev.java.net/}.
\I JConsole \tw{-Dcom.sun.management.jmxremote} \tw{<} 6.
\I VisualGC for VisualVM.
\I Throughput collector lacks tenuring distribution in VisualGC.
\I \XX{+PrintCompilation}.
\I \XX{Permsize=}.
\I \XX{MaxPermSize=}.
\I MBeans.
\I JMX.
\I jstack.
\I Shorter path length.
\I Caller-Callees.
\I JVM-System.
\I JSR-133.
\I Memory barrier.
\I Member fence.
\I Systemic requirements.
\I Performance tuning assumed phases:
\II Initialisation phase.
\II Steady state phase.
\II Summary phase.
\I Application Systemic Requirements (ASRs):
\II Availability.
\II Manageability.
\II Throughput.
\II Latence \& responsiveness.
\II Memory footprint.
\II Startup time.
\I \tw{-d64}.
\I Minor GC Reclamation Principal.
\I GC Maximum Memory Prinicipal.
\I 2 of 3 GC Tuning Principal.
\bye
