\subsection{Minutes}

\item{27/04/04} Initial Meeting.
[All members present or provided with meeting outcomes]

\itemitem{Duration:} 30 minutes

Allocated roles to each group member. 

\itemitem{Luke:} Team leader
\itemitem{Dion:} Reference checker
\itemitem{Pete:} Compiler
\itemitem{Geoff:} Record keeper

A brief brainstorm as to relevant areas for research was conducted.
Arrangements were made for each member to conduct research during the following
week and report back at the next meeting.

\item{04/05/04} Research Meeting.
[All members present]

\itemitem{Duration:} 45 minutes

Each group member provided group with details of their research. Information
was shared amongst team and a list of the most relevant research material was
agreed upon.

At this point group members each chose a section of the report to prepare a
draft answer for, agreeing to have the draft completed prior to the next
meeting.

\item{11/05/04} First Draft Meeting
[All members present]

\itemitem{Duration:} 60 minutes

All group members had successfully submitted drafts prior to this meeting, so
a draft of the report was distributed during the meeting. Strengths and
weaknesses present within the draft were addressed, and areas which needed to
be improved upon prior to the next meeting were agreed upon.

\item{18/05/04} Draft Revision Meeting
[All members present]

\itemitem{Duration:} 20 minutes

All group members had successfully submitted drafts prior to this meeting, so a
draft of the report was distributed during the meeting. Strengths and
weaknesses present within the draft were addressed, and areas which needed to
be improved upon prior to the next meeting were agreed upon.

It was agreed that each team member would revise their sections of the report,
making the decided upon changes. Revised drafts were to be completed ASAP and
distributed. References were to be forwarded to the reference checker for
verification, and finalised report sections were to be submitted to the team
compiler. 

\item{24/05/04} Final Report and Evaluation Meeting
[All members present]

\itemitem{Duration:} 30 minutes

A finished copy of the final report was developed prior to this meeting. Group
members reviewed the finished product and no flaws were identified. It was
agreed that our time management had been relatively successful, and that the
team had functioned efficiently over the duration of the report production.

Minutes for all group meetings were finalised and added to the report upon the
completion of the final team meeting.

Aside from these meetings, numerous email messages were exchanged between
group members during the production of this report. These allowed group
progress to be constantly monitored, in addition to being checked at regular
team meetings.
