\font\titlefont=cmr10 at 16pt

\def \url #1 {\tt #1 \hfill \rm}

\def \title #1 {\centerline{\titlefont #1}}

\def \RCS$#1: #2 ${\expandafter\def\csname RCS#1\endcsname{#2}}


\newcount\itemnum \itemnum=0

\newcount\subitemnum

\def\items { \advance \itemnum by 1
	\item {
		\bf \the\itemnum)
	}
}

\def\resetsubitemnum { \subitemnum=0 }

\def\subitems { \advance \subitemnum by 1
	\itemitem {
		\bf \the\itemnum.\the\subitemnum)
	}
}

\parskip 12 pt

\def \navigate #1 { Navigate to the {\bf ``#1''} page. }

\title { IT Students Association web site evaluation: }

\centerline {\sevenrm \RCSId }

\items What web browser is being used to evaluate the web site?

\bigskip
\hrule

\items Go to the following URL \url { http://www.flameburst.com/CSCI102/ }
\resetsubitemnum
\subitems Does the page load in a timely manner?

\items \navigate { About Us }
\resetsubitemnum
\subitems Do pictures of the associations members appear without any problems?

\items \navigate { Location }
\resetsubitemnum
\subitems Does a map of the University of Wollongong appear?

\items \navigate { Activities }
\resetsubitemnum
\subitems Was the content set out in an appealing manner?

\items \navigate { Contact Us }
\resetsubitemnum
\subitems Attempt to send a message to the webmaster.
\subitems Did a message appear stating that the message was sent to the desired receipent?

\items \navigate { Guest Book }
\resetsubitemnum
\subitems Add an entry to the Guest Book.
\subitems Did the entry appear at the top of the Guest Book?

\items \navigate { Forum }
\resetsubitemnum
\subitems Are you sent to the following URL \url { http://pub206.ezboard.com/bcsci102 }?

\items Rate the loading speed of the web site on the scale below:

\bigskip
\settabs 7 \columns
\+ & Abysmal & Poor & Moderate & Good & Excellent \cr

\items Rate the intuitiveness of the web site navigability on the scale below:

\bigskip
\settabs 7 \columns
\+ & Abysmal & Poor & Moderate & Good & Excellent \cr

\items Rate the appeal of the web site on the scale below:

\bigskip
\settabs 7 \columns
\+ & Abysmal & Poor & Moderate & Good & Excellent \cr

\items Rate the ease of use of the web site on the scale below:

\bigskip
\settabs 7 \columns
\+ & Abysmal & Poor & Moderate & Good & Excellent \cr

\items Did the web page have any visible artifacts after being rendered? If so, please describe them.

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items Please comment on the visual presentation of the web site.

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items Please comment on the content of the web site.

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items What improvements could you suggest to increase the quality of your experience of the web site with your particular browser?

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items Did you have any problems navigating the web site? If so, please elabourate.

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items Could you easily navigate from one web page to another? If no, explain why not.

\bigskip
\hrule

\bigskip
\hrule

\bigskip
\hrule

\items Were the colours used on the web site easy on the eye?

\bye
