
\font \mainfont=cmr12
\font \secfont=cmbx12
\font \titlefont=cmr14

\newcount \footnotes \footnotes=0

\def \footnoter#1{\advance\footnotes by 1 \footnote{$^{\the\footnotes}$}{\rm #1}}

\def \RCS$#1: #2 ${\expandafter\def\csname RCS#1\endcsname{#2}}


\newcount\itemnum \itemnum=0

\def\items {
	\advance \itemnum by 1
	\itemitem {
		\bf \the\itemnum)
	}
}

\def \section#1 {
	\vskip 12 pt 
	\leftline {
		\secfont #1
	} 
	\nobreak 
}

\parskip 12 pt
\parindent 24 pt

\centerline {
	\titlefont Report on the conducted testing of web technologies
	employed in the Association web site.
} 

\centerline{\sevenrm \RCSId }

\vskip 24 pt

\mainfont

\section{Introduction.}

This report will outline the results of the employed tests carried out to
ascertain the adherence to W3C\footnoter{http://www.w3.org/} standards.

In particular, that all pages adheres to the standards set out for the HTML
mark up language, as has been tested by the W3C
Validator\footnoter{http://validator.w3.org/} and that all Cascading Style
Sheets adhere to their standards as tested by the CSS
Validator\footnoter{http://jigsaw.w3.org/css-validator/}.

To aid in diagnosing possible problems between different industry web browsers,
a small survey was conducted with the resulting forms attached. A summary of
the findings of the survey will be included in this report.

\section{HTML Validation}

The following URLs that compose the web site were validated with the W3C HTML
Validator:

\parskip 0 pt
\items http://www.flameburst.com/CSCI102/
\items http://www.flameburst.com/CSCI102/AboutUs.html
\items http://www.flameburst.com/CSCI102/Location.html
\items http://www.flameburst.com/CSCI102/Activities.html
\items http://www.flameburst.com/CSCI102/Activities.html
\items http://www.flameburst.com/CSCI102/GuestBook.aspx
\parskip 12 pt
\itemnum=0

According to the HTML Validator, none of the HTML documents in the Associations
web site adhered to any of the possible HTML standards. Appendix A has the list
of links to the results pages for each of the above URL.

As none of the pages adheres to the HTML standards as set out by the W3C, it
can easily be shown that there will be problems in the display of the web site
under different browsers as they will all render web pages that do not adhere
to the standards in their own fashion. This was the case when a number of users
were asked to take a survey of the web site.

\section{CSS Validation}

The following URL is the Cascading Style Sheet file that is used by all the
pages in the Associations web site:
http://www.flameburst.com/CSCI102/csci102.css

Fortunately, the Cascading Style Sheet that is used in the Associations web site
is valid according to the standards set out by the W3C. This will ensure that
any browser that adheres to the same set of CSS standards, as the majority of
main stream industry web browsers do, will render the CSS portions in a
consistent manner.

\section{User Survey Summary}

A small user survey was conducted, giving a view of how a variety of web
browsers render the web site. The survey participants were urged to offer
comments and answer a few questions related to how the page is displayed.

The following is a list of the browsers that were included in the survey:

\parskip 0 pt

\items Netscape Mozilla (versions 1.0 \& 1.3)\footnoter{http://www.mozilla.org/}
\items Netscape Communicator 4.77\footnoter{http://channels.netscape.com/ns/browsers/default.jsp}
\items Microsoft Internet Explorer\footnoter{http://www.microsoft.com/catalog/display.asp?subid=22\&site=10829}
\items Opera 6.03\footnoter{http://www.opera.com/}
\items KDE\footnoter{http://www.kde.org/} Konqueror\footnoter{http://www.konqueror.org/}

\parskip 12 pt
\itemnum=0

There was mixed information gathered, there was one consistent comment from
all the participants, that the web site was entirely too green.

All except one survey stated that the web site loaded in a timely manner. This
is a good indication as one of the primary goals of the web site was to have a
fast loading time.

There was one serious problem uncovered during the survey. It was shown that
the guest book was not parsed for malicious mark up in the text fields. Now, the
guest book is entirely populated by small and annoying Java script pop-ups that
can not be ceased without exiting the browser. In one case, the user had to
forcefully terminate their browser as it was locked in a loop of Java script
pop-ups. This is a serious problem as malicious code could be inserted in to
the guest book causing harm to someone's computer security.

There were some rendering problems in regards to the menu which is supposed to
stay at the top left hand corner of the web page, in some browsers, most
notably Opera and Konqueror, the menu would exist halfway down the page. In
either way, this caused problems as the user would have to scroll from their
current position to the menu if they chose to navigate to another part of the
site.

I would have been better if the menu floated in the middle of the left part
of the users web browser window, thus, where ever that user was in a page, the
menu would always be accessible.

\section{Conclusion:}

The findings of this report are that the web site does not adhere to the W3C
HTML Standards which may cause rendering artifacts. The Cascading Style Sheet
used is compliant with the W3C standards, however as the HTML is not, this is
a moot concern.

The web sites content could be improved, with the greatest concern that the
colour scheme is all too green.

\section{Appendix A: HTML Validation results}

The following is a list of the URLs for the W3C HTML Validation reports:

\parskip 0 pt
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2F}
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2FAboutUs.html}
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2FLocation.html}
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2FActivities.html}
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2FContact.aspx}
\items \sevenrm{http://validator.w3.org/check?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2FGuestBook.aspx}
\parskip 12 pt
\itemnum=0

\section{Appendix B: CSS Validation results}

\fiverm http://jigsaw.w3.org/css-validator/validator?uri=http\%3A\%2F\%2Fwww.flameburst.com\%2FCSCI102\%2Fcsci102.css\&warning=1\&profile=css2

\bye
